### 2017-03-11 paper.tex
Init Document Structure

\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{sectsty}
\usepackage{authblk}
\usepackage{textcomp}
\renewcommand{\refname}{}

\setlength{\paperheight}{297mm}
\setlength{\paperwidth}{210mm}
\setlength{\voffset}{-12mm}
\setlength{\topmargin}{0mm}
\setlength{\headsep}{8mm}
\setlength{\headheight}{10mm}
\setlength{\textheight}{235mm}
\setlength{\hoffset}{-4mm}
\setlength{\textwidth}{166mm}
\setlength{\oddsidemargin}{0mm}
\setlength{\evensidemargin}{0mm}
\setlength{\marginparwidth}{0mm}
\setlength{\marginparpush}{0mm}
\setlength{\columnsep}{6mm}
\setlength{\parindent}{6mm}
\setlength{\parskip}{2mm}

%% insert table
%% use as \tabin{size_in_mm}{label}{caption}{table_data}
\newcounter{tabcounter}
\def\tabin #1#2#3#4{
\refstepcounter{tabcounter} \label{#2}
\[ \makebox[#1][c]{#4} \]
%\vspace{0mm}
\begin{center}
  \parbox{7cm}{{\bf Table \arabic{tabcounter}:}\quad {\it #3 } } \\
\end{center}
}

\title{\LARGE
Title
}

\author[*]{\large
{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
\author[**]{\large
{\bf Chung-Fan Yang}\thanks{E24026048@mail.ncku.edu.tw}}
\affil[*]{Department of Computer Science and Information Engineering,
\newline
National Cheng Kung University, Taiwan
\newline
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\affil[**]{Department of Electrical and Electronic Engineering,
\newline
National Cheng Kung University, Taiwan
\newline
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\date{}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\vspace{10mm}

\begin{multicols}{2}

\section{Introduction}

\section{Related Work}

\section{Methodology Environment}

\section{Methodology Result}

\bibliographystyle{unsrt}
\begin{thebibliography}{9}%use this if you have <=9 bib refs
	\bibitem {rtai}{\it https://www.rtai.org/}
\end{thebibliography}

\end{multicols}
\end{document}

### 2017-03-11 paper.tex
Draft of third part

@@
 
+    Based on the works presented above, we had found out several problems in common methodology method used currently.
+    First, the methodology tool, e.g. cyclictest, is over-simplified. It only gives the wakeup latency measurements,
+    which sometimes is not the main or only performance bottle-neck of a real-time system. Also, general profiling
+    tools, e.g. perf, is typically utilizing the sampling methodology method, lacking high fidelity, all-recorded
+    profiling result of the target system in microsecond scale, which is usually seen in real-time system tuning. In
+    addition, the behavior and loading characteristic of work-load used during test, e.g. hackbench, stress, etc. are
+    far from the real target applications. These problems not only would significantly reduce the effectiveness of
+    tuning target system, but also will cause actual hazards, harming the real-time performance, obscure.
+
+    Our approach to counter these problems includes a new profiling method and a test work-load, which is able to
+    represent the target real-time application. The new profiling tool is derived from paper A Decade of Wasted Cores,
+    published in EuroSys 2016. In A decade of Wasted Cores, authors have development a profiler which instruments the
+    scheduler of Linux Kernel, extracting scheduling information. Based on this work we have extended the ability of the
+    profiler to extract the running entity of each core of the target system also the context-switching information,
+    including time and target process id (PID). This enabled us to record and collect kernel scheduling information,
+    running PID of each processor core fully during the execution of work-load. The recorded data resolution is based on
+    the timer resolution of kernel scheduler. On x86-64 and ARM platform, the resolution could achieve sub-microsecond
+    level. This gives us the advantage to justify when would the processor core executes the real-time task, how
+    work-loads were scheduled by the kernel scheduler, and random scheduling events. This level of detail could not be
+    achieved with the previous mentioned tools, which only utilizes the processor's performance measurement unit (PMU),
+    lacking the fidelity requires during the tuning of real-time system.
+
+    We also created a testing framework which resembled target application execution behavior, this application could be
+    utilized as the testing work-load during methodology. In addition, application created using this framework has the
+    ability to be compiled either as user-space program or kernel module. This would grants us the ability to observe
+    the characteristic of target application execution in both user-space and kernel-space. This would gives the insight
+    of system-call and user-space I/O overhead. In addition, this framework, while executing, would do a series of
+    identically executions and record the execution time of each turn. These data can be used to determined the
+    execution jitter of the application on the real-time system, which besides wakeup latency. This could be used to
+    reflect to the system-call overhead on the system.
+
+    In aid of these developed tools and work presented above, we proposed a high accuracy methodology system, and apply
+    this on various platform, including x86-64 and ARM.
+
 \section{Methodology Result}

### 2017-03-19 paper.tex
Change Title of section 3 and 4
Draft of section 4 and reference
Updated tex source to use IEEEtrans format template

@@
-\documentclass[10pt,a4paper]{article}
+\documentclass[conference]{IEEEtran}
 \usepackage[english]{babel}
@@
 \usepackage{url,hyperref,graphicx,float,times}
-\usepackage{sectsty}
-\usepackage{authblk}
+%\usepackage{sectsty}
+%\usepackage{authblk}
 \usepackage{textcomp}
-\renewcommand{\refname}{}
+\usepackage{cite}
+% \graphicspath{{../pdf/}{../jpeg/}}
+% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\usepackage[caption=false,font=footnotesize]{subfig}
 
-\setlength{\paperheight}{297mm}
-\setlength{\paperwidth}{210mm}
-\setlength{\voffset}{-12mm}
-\setlength{\topmargin}{0mm}
-\setlength{\headsep}{8mm}
-\setlength{\headheight}{10mm}
-\setlength{\textheight}{235mm}
-\setlength{\hoffset}{-4mm}
-\setlength{\textwidth}{166mm}
-\setlength{\oddsidemargin}{0mm}
-\setlength{\evensidemargin}{0mm}
-\setlength{\marginparwidth}{0mm}
-\setlength{\marginparpush}{0mm}
-\setlength{\columnsep}{6mm}
-\setlength{\parindent}{6mm}
-\setlength{\parskip}{2mm}
-
-%% insert table
-%% use as \tabin{size_in_mm}{label}{caption}{table_data}
-\newcounter{tabcounter}
-\def\tabin #1#2#3#4{
-\refstepcounter{tabcounter} \label{#2}
-\[ \makebox[#1][c]{#4} \]
-%\vspace{0mm}
-\begin{center}
-  \parbox{7cm}{{\bf Table \arabic{tabcounter}:}\quad {\it #3 } } \\
-\end{center}
-}
-
-\title{\LARGE
-Title
-}
-
-\author[*]{\large
-{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
-\author[**]{\large
-{\bf Chung-Fan Yang}\thanks{E24026048@mail.ncku.edu.tw}}
-\affil[*]{Department of Computer Science and Information Engineering,
-\newline
-National Cheng Kung University, Taiwan
-\newline
-No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
-\affil[**]{Department of Electrical and Electronic Engineering,
-\newline
-National Cheng Kung University, Taiwan
-\newline
-No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
-\date{}
+\usepackage{url}
 
 \begin{document}
+
+\title{Title}
+
+\author{\IEEEauthorblockN{Ching-Chun (Jim) Huang}
+\IEEEauthorblockA{Department of Computer Science and\\Information Engineering\\
+National Cheng Kung University, Taiwan\\
+No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
+Email: jserv@ccns.ncku.edu.tw}
+\and
+\IEEEauthorblockN{Chung-Fan Yang}
+\IEEEauthorblockA{Department of Electrical Engineering\\
+National Cheng Kung University, Taiwan\\
+No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
+Email: E24026048@mail.ncku.edu.tw}}
 
@@
 
-\vspace{10mm}
-
-\begin{multicols}{2}
-
 \section{Introduction}
@@
 
-\section{Methodology Environment}
+\section{Methodology}
 
     Based on the works presented above, we had found out several problems in common methodology method used currently.
-    First, the methodology tool, e.g. cyclictest, is over-simplified. It only gives the wakeup latency measurements,
-    which sometimes is not the main or only performance bottle-neck of a real-time system. Also, general profiling
-    tools, e.g. perf, is typically utilizing the sampling methodology method, lacking high fidelity, all-recorded
-    profiling result of the target system in microsecond scale, which is usually seen in real-time system tuning. In
-    addition, the behavior and loading characteristic of work-load used during test, e.g. hackbench, stress, etc. are
-    far from the real target applications. These problems not only would significantly reduce the effectiveness of
-    tuning target system, but also will cause actual hazards, harming the real-time performance, obscure.
+    First, the methodology tool, e.g. cyclictest \cite{cyclictest} \cite{rt-tests}, is over-simplified. It only gives the wakeup latency
+    measurements, which sometimes is not the main or only performance bottle-neck of a real-time system. Also, general
+    profiling tools, e.g. perf \cite{perf}, is typically utilizing the sampling methodology method, lacking high
+    fidelity, all-recorded profiling result of the target system in microsecond scale, which is usually seen in
+    real-time system tuning. In addition, the behavior and loading characteristic of work-load used during test, e.g.
+    hackbench, stress \cite{rt-tests}, etc. are far from the real target applications. These problems
+    not only would significantly reduce the effectiveness of tuning target system, but also will cause actual hazards,
+    harming the real-time performance, obscure.
 
@@
     represent the target real-time application. The new profiling tool is derived from paper A Decade of Wasted Cores,
-    published in EuroSys 2016. In A decade of Wasted Cores, authors have development a profiler which instruments the
-    scheduler of Linux Kernel, extracting scheduling information. Based on this work we have extended the ability of the
-    profiler to extract the running entity of each core of the target system also the context-switching information,
-    including time and target process id (PID). This enabled us to record and collect kernel scheduling information,
-    running PID of each processor core fully during the execution of work-load. The recorded data resolution is based on
-    the timer resolution of kernel scheduler. On x86-64 and ARM platform, the resolution could achieve sub-microsecond
-    level. This gives us the advantage to justify when would the processor core executes the real-time task, how
-    work-loads were scheduled by the kernel scheduler, and random scheduling events. This level of detail could not be
-    achieved with the previous mentioned tools, which only utilizes the processor's performance measurement unit (PMU),
-    lacking the fidelity requires during the tuning of real-time system.
+    published during EuroSys 2016 \cite{Lozi:2016:LSD:2901318.2901326}. In A decade of Wasted Cores, authors have
+    development a profiler which instruments the scheduler of Linux Kernel, extracting scheduling information. Based on
+    this work we have extended the ability of the profiler to extract the running entity of each core of the target
+    system also the context-switching information, including time and target process id (PID). This enabled us to record
+    and collect kernel scheduling information, running PID of each processor core fully during the execution of
+    work-load. The recorded data resolution is based on the timer resolution of kernel scheduler. On x86-64 and ARM
+    platform, the resolution could achieve sub-microsecond level. This gives us the advantage to justify when would the
+    processor core executes the real-time task, how work-loads were scheduled by the kernel scheduler, and random
+    scheduling events. This level of detail could not be achieved with the previous mentioned tools, which only utilizes
+    the processor's performance measurement unit (PMU), lacking the fidelity requires during the tuning of real-time
+    system.
 
@@
 
+\section{Experiment}
+
     In aid of these developed tools and work presented above, we proposed a high accuracy methodology system, and apply
-    this on various platform, including x86-64 and ARM.
+    this on various platform, including x86-64 and ARM. The experiment platform is running Linux Kernel version 4.4 with
+    PR\textunderscore RT \cite{preemptrt} patch and it's built with buildroot \cite{buildroot} package.
 
-\section{Methodology Result}
+\subsection{Profiling Tool Evaluation}
 
-\bibliographystyle{unsrt}
-\begin{thebibliography}{9}%use this if you have <=9 bib refs
-	\bibitem {rtai}{\it https://www.rtai.org/}
-\end{thebibliography}
+    With the newly developed profiling tool, we were able to capture a specified task's execution period in microsecond
+    level. To evaluate this we execute various work-load on the experiment platform, Altera Cyclone5 SoC development
+    kit, hosting dual core ARM Cortex-A9 processor with 1Gb memory. First, a cyclistest executing solely is shown in
+    figure 1. The area high lighted with gray are the real-time task being executed by cpu, with black bars marking the
+    switching-in and switching-out point. Also, cooperating with the heat map of scheduler run-queue size shown in
+    figure 2, we can tell that whether other tasks arrive in the scheduler together with real-time task with short
+    inter-arrival time. In these circumstances, preemption and re-scheduling might occur. While testing how different
+    loading conditions interference the real-time task, we observed that the jitter will increase when the number of
+    tasks in system (real-time tasks and work-load tasks) increases. Diving into this problem, we modified the profiling
+    tool to record the scheduling duration of real-time task. The result of profiling is in figure 3-a and 3-b, showing
+    that in no-load and mild-load condition, the schedule duration are less than 10us, but with heavy-load condition,
+    shown in figure 3-c, the schedule duration will ramp up to 30us in maximum. This hints us that although the CFS
+    scheduler is able to determine which task to be switched-in in O(1) time \cite{cfs}, additional overhead exist. This overhead
+    would increase alone with the system's loading condition.
 
-\end{multicols}
+\subsection{Comparison of Kernel and User-space Execution}
+
+\subsubsection{Profiling System Call Overhead}
+
+    With our work-load framework, we constructed a work-load called mctest, which resemble a real-time robot control
+    system. This algorithm includes various computational heavy code and system-calls. Putting this work-load into
+    execution on Freesacle i.mx6 Sabre platform which hosted 4 core ARM Cortex-A9 processor with 1Gb memory. We also
+    enabled tickless feature \cite{tickless} of Linux kernel and isolate CPU 1 from scheduler use \cite{isolatedcpu}.
+    Putting mctest on isolated and tickless CPU 1, we recorded the execution jitter. The result is shown in figure 4.
+    With this result, we could suggest that the system call generates a large amount of jitter. And the overhead of
+    system call will increase alone with the loading condition of the system. Figure 5 shows the execution jitter with
+    load. As a result, rewriting real-time application as a kernel module is the only feasible approach.
+
+\subsubsection{Kernel Mode Linux}
+
+    While rewriting the real-time application in kernel module would reduce the execution jitter. This approach is
+    difficult and tedious. Thus, it's not feasible to be wildly deployed. As the source of jitter, system call, has been
+    identified. We applied an different approach, Kernel Mode Linux (KML) \cite{KML} \cite{KMLConf}. KML enables the
+    ability for specified user-space program to access kernel address space directly. Thus, system calls become jump
+    instructions, not instruction trapping the processor. In addition, we have also rewired system calls, which have
+    vDSO implementations \cite{vDSO}, to use vDSO implementation via KML. This approach, executing in the same
+    environment as above section, could reduce the user-space execution jitter comparable to kernel module approach,
+    shown in figure 6. Therefore, KML have enable the ability to write real-time application user-space and exploit
+    kernel-space performance to it.
+
+\section{Conclusion}
+
+    We have evaluated the real-time behavior of Linux by profiling kernel scheduler and measuring the latency of various
+    kernel variants. An intensive interrupt load can cause long OS latencies due to the design of the interrupt
+    processing mechanism. We proposed new tools to visualize task scheduling in fine-grained scale(microsecond level).
+    This enabled us not only focusing on interrupt latency, but also scheduler durations, lock, and etc. It would thus
+    be highly desirable to combine existing techniques, e.g KML, isolated CPU, tickless kernel, to improve task
+    responsiveness under various target application characteristics, on top of PREEMPT\textunderscore RT.
+
+\bibliographystyle{IEEEtran}
+\bibliography{references}
+
 \end{document}

### 2017-03-25 paper.tex
Update Section 3 and 4

--- 2017-03-11 paper.tex
@@
 \usepackage{url,hyperref,graphicx,float,times}
-\usepackage{sectsty}
-\usepackage{authblk}
+%\usepackage{sectsty}
+%\usepackage{authblk}
 \usepackage{textcomp}
-\renewcommand{\refname}{}
+\usepackage{cite}
+% \graphicspath{{../pdf/}{../jpeg/}}
+% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\usepackage[caption=false,font=footnotesize]{subfig}
 
-\setlength{\paperheight}{297mm}
-\setlength{\paperwidth}{210mm}
-\setlength{\voffset}{-12mm}
-\setlength{\topmargin}{0mm}
-\setlength{\headsep}{8mm}
-\setlength{\headheight}{10mm}
-\setlength{\textheight}{235mm}
-\setlength{\hoffset}{-4mm}
-\setlength{\textwidth}{166mm}
-\setlength{\oddsidemargin}{0mm}
-\setlength{\evensidemargin}{0mm}
-\setlength{\marginparwidth}{0mm}
-\setlength{\marginparpush}{0mm}
-\setlength{\columnsep}{6mm}
-\setlength{\parindent}{6mm}
-\setlength{\parskip}{2mm}
-
-%% insert table
-%% use as \tabin{size_in_mm}{label}{caption}{table_data}
-\newcounter{tabcounter}
-\def\tabin #1#2#3#4{
-\refstepcounter{tabcounter} \label{#2}
-\[ \makebox[#1][c]{#4} \]
-%\vspace{0mm}
-\begin{center}
-  \parbox{7cm}{{\bf Table \arabic{tabcounter}:}\quad {\it #3 } } \\
-\end{center}
-}
-
-\title{\LARGE
-Title
-}
-
-\author[*]{\large
-{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
-\author[**]{\large
-{\bf Chung-Fan Yang}\thanks{E24026048@mail.ncku.edu.tw}}
-\affil[*]{Department of Computer Science and Information Engineering,
-\newline
-National Cheng Kung University, Taiwan
-\newline
-No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
-\affil[**]{Department of Electrical and Electronic Engineering,
-\newline
-National Cheng Kung University, Taiwan
-\newline
-No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
-\date{}
+\usepackage{url}
 
 \begin{document}
+
+\title{Title}
+
+\author{\IEEEauthorblockN{Ching-Chun (Jim) Huang} \IEEEauthorblockA{Department of\\Computer Science and Information
+Engineering\\National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\ Email:
+jserv@ccns.ncku.edu.tw} \and \IEEEauthorblockN{Chung-Fan Yang} \IEEEauthorblockA{Department of Electrical Engineering\\
+National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\ Email:
+E24026048@mail.ncku.edu.tw}}
 
@@
 
-\section{Methodology Environment}
+\section{Methodology}
 
-\section{Methodology Result}
+    Based on the works presented above, we have methods to measure the overall wake-up latency and context-switch
+    latency, using cyclictest and lmbench. Also, it's able to show that the CFS algorithm has O(1) complexity on
+    selecting next task, giving static latency. Thus, overall  and parts of latency of a Linux system can be determined,
+    but the measurement methodology and tool of scheduler latency, shown in figure \ref{sec:latency_timeline}, are
+    lacking. Therefore, we developed a evaluation tool of scheduler duration jitter, based on methodology method of A
+    Decade of Wasted Cores \cite{Lozi:2016:LSD:2901318.2901326}. This methodology method enabled us to record the
+    scheduler states including, executing process ID (PID), PID in scheduler run-queue, context switch points, timer
+    interrupt execution, scheduling events, etc. on per processor core basis. This methodology method differs from
+    profiling based methodology tools, e.g. perf \cite{perf}, lacking high fidelity, all-recorded profiling result of
+    the target system. Our proposed tool can do full-detailed record in microsecond scale on x86-64 and ARM system,
+    which is able to capture the impact to real-time performance of occasional short-burst scheduler events, which only
+    last less that 10us. These events are mostly not shown in the result of sampling based measurement which focus on
+    average-case execution time(ACET). By analyzing full-detailed record, we are able to not only capture the worst-case
+    execution time (WCET), but also understand the cause of these incidents.
 
-\bibliographystyle{unsrt}
-\begin{thebibliography}{9}%use this if you have <=9 bib refs
-	\bibitem {rtai}{\it https://www.rtai.org/}
-\end{thebibliography}
+    In addition, the behavior and loading characteristic of typical work-load used during test in above works, e.g.
+    hackbench, stress \cite{rt-tests}, etc. are far from the real-world real-time applications. These problems not only
+    would reduce the significant of target system jitter measurement, but also will make incidents, harming the
+    real-time performance, obscure. In result of this frustration, we also created a testing framework hosing an
+    algorithm which resembled a real-time robot control system execution behavior, named mctest. This work-load
+    application has the ability to be compiled either as user-space program or kernel module, provides observation of
+    the characteristic of target application execution in both user-space and kernel-space. This would gives the insight
+    of system-call and user-space I/O overhead, which does not exist in kernel module. In addition, mctest would do a
+    series of identically executions and record the execution time of each turn. These records can be used to determined
+    the execution jitter of the application on the real-time system, which besides wakeup latency. This could be used to
+    reflect to the system-call overhead of the system. We have been utilizing mctest as the testing work-load and jitter
+    measurement tool during methodology.
 
-\end{multicols}
+    \begin{figure} \centering \includegraphics[width=3.0in]{img/f1.png} \caption{Task Wake-up Latency}
+    \label{fig:latency_timeline} \end{figure}
+
+\section{Experiment}
+
+    In aid of these developed tools and work presented above, we did multiple experiments and measurement of 2 ARM
+    Cortex-A9 based platform, shown in table I. These platforms are selected as CMP based ARM system are emerging and
+    being used in a wide field of applications. These systems are running buildroot \cite{buildroot} built Linux with
+    kernel version 4.4 and PR\textunderscore RT \cite{preemptrt} patches.
+
+    \begin{table*}[] \centering \caption{Experiment Platforms} \begin{tabular}{|l|c|c|} \hline Platform Name & Altera
+        SoC FPGA Development Kit & Freescale i.mx6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
+        \hline Memory & 1 GB & 1 GB \\ \hline Additional configuration & None & \begin{tabular}[c]{@{}c@{}}L2 Cache
+        locked down to CPU1,\\ Isolated CPU1,\\ Enabled tickless on CPU1 \\ Real-time task pinned to CPU1 \end{tabular}
+    \\ \hline \end{tabular} \end{table*}
+
+    Our experiment begins with known tuning practices which includes processor isolation \cite{isolatedcpu}, tickless
+    feature of kernel \cite{tickless}, L2 cache lockdown. We compared the measurement result of mctest with and without
+    these tuning techniques on Freesacle i.mx6 Sabre platform. Measurement results are shown in figure 2 to 4, verifying
+    the effectiveness of these known tuning techniques and providing results as a baseline. We are able to see the WECT
+    with and without tuning are 100us and 100us. This gives us the hint that the scheduling  would harms the real-time
+    performance. This scheduling overhead could be separated into 2 parts, scheduler overhead and cache contention on
+    SMP system. With L2 Cache lockdown technique we are able to mitigate most of the cache contention, but still
+    resulting some degree of jitter about 100us
+
+\subsection{System Call Overhead and Kernel Mode Linux}
+
+    In addition, we compared the user-space mctest result with kernel space measurement, shown in figure 6 and 7 with
+    WECT of 50us and 50us. With these result, we are able to identify the sources of jitter are system calls. To
+    mitigate these, we first proposed to rewrite real-time applications as kernel modules. But this is tedious and
+    making the debugging process difficult. Thus, we proposed a second approach, Kernel Mode Linux(KML) \cite{KML}
+    \cite{KMLConf}. KML enables the ability for specified user-space program running in kernel memory space. Thus,
+    system calls become jump instructions, not instruction trapping the processor. Also, this would mitigate the cache
+    contention while switching in and out the kernel during system call. In addition, we have also rewired system calls,
+    which have vDSO implementations \cite{vDSO}, to use vDSO implementation via KML. The result of user-space program
+    running in KML is shown in figure 8 with WECT of 20us, which proving the effectiveness of jitter mitigation from
+    KML.
+
+\subsection{Scheduler Overhead Measurement}
+
+    Identifying that scheduler is also a source of jitter, we applied our proposed scheduler profiling tool to evaluate
+    and identify of which part of the scheduling process is the source of jitter. Knowing the IRQ latency, and
+    context-switching latency, we would like to evaluate the scheduler duration. Traditionally, the latency of this part
+    is considered static with the CFS algorithm complexity, designed to be O(1), but real measurement result are
+    lacking. Thus, we set our proposed profiler to record the increment of scheduler run-queue and scheduler
+    context-switching events with switched-to PID of each processors. A analyzer will process the recorded data and
+    gives out the scheduler duration of a specified process, enabling us the understand the scheduling of real-time task
+    in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure 9.
+    The latency could be considered static with maximum 10us. This result matches traditional considerations, but with
+    the interference from other work-load, the jitter will start to emerge.
+
+\subsubsection{Overloaded System}
+
+    We created additional work-load, executing alone with cyclictest during profiling session. We created a mild loading
+    condition, which has 3 stress threads, and a heavy loading condition, which has 8 stress threads. The result of mild
+    loading condition is shown in figure 10. This result also exhibits a mostly static scheduler duration with seldom
+    jitter with maximum of 20us. But putting the system in to heavy loading condition, the result, shown in figure 11
+    exhibits random jitter from 10us to 30us. The spread of distribution of scheduler duration, shown in figure 12,
+    would become wilder. This informs us that the scheduler duration is not a static value and will increase alone with
+    the system's load. Also informs that the scheduler duration contains but not only contains CFS algorithm task
+    selection process which is proved to be O(1).
+
+\subsubsection{Short Inter-Arrival Time}
+
+    We also captured large jitter of scheduler duration on a mild loaded system. The experiment is running mctest with
+    cyclictest. We pinned kernel module mctest to use first processor, causing cyclictest real-time thread and main
+    thread being scheduler onto second processor. On most of the time, this execution schema results the same result as
+    cyclictest executing solely in the system. But on some occasions, the cyclictest main thread would be waken-up and
+    enter run-queue with short inter-arrival time against the cyclictest real-time thread, which was also being
+    waken-up. When this event happened, the scheduler duration will raise to 30us. This result, shown in figure 13 hints
+    us that not only long term overload system would exhibit large scheduler duration, but also short burst a
+    overloading condition during the real-time task scheduling and execution would cause the scheduler duration to
+    raise.
+
+\section{Conclusion}
+
+    We have evaluated the real-time behavior of Linux by profiling kernel scheduler and measuring the latency of various
+    kernel variants. An intensive interrupt load can cause long OS latencies due to the design of the interrupt
+    processing mechanism. We proposed new tools to visualize task scheduling in fine-grained scale(microsecond level).
+    This enabled us not only focusing on interrupt latency, but also scheduler durations, lock, and etc. It would thus
+    be highly desirable to combine existing techniques, e.g KML, isolated CPU, tickless kernel, to improve task
+    responsiveness under various target application characteristics, on top of PREEMPT\textunderscore RT.
+
+\bibliographystyle{IEEEtran}
+\bibliography{references}
+
 \end{document}

### 2017-03-25 paper.tex
Insert images

@@
     selecting next task, giving static latency. Thus, overall  and parts of latency of a Linux system can be determined,
-    but the measurement methodology and tool of scheduler latency, shown in figure \ref{sec:latency_timeline}, are
+    but the measurement methodology and tool of scheduler latency, shown in figure \ref{fig:latency_timeline}, are
     lacking. Therefore, we developed a evaluation tool of scheduler duration jitter, based on methodology method of A
@@
 
-    \begin{figure} \centering \includegraphics[width=3.0in]{img/f1.png} \caption{Task Wake-up Latency}
+    \begin{figure} \centering \includegraphics[width=3.5in]{img/latency_timeline.png} \caption{Task Wake-up Latency}
     \label{fig:latency_timeline} \end{figure}
@@
     feature of kernel \cite{tickless}, L2 cache lockdown. We compared the measurement result of mctest with and without
-    these tuning techniques on Freesacle i.mx6 Sabre platform. Measurement results are shown in figure 2 to 4, verifying
-    the effectiveness of these known tuning techniques and providing results as a baseline. We are able to see the WECT
-    with and without tuning are 100us and 100us. This gives us the hint that the scheduling  would harms the real-time
-    performance. This scheduling overhead could be separated into 2 parts, scheduler overhead and cache contention on
-    SMP system. With L2 Cache lockdown technique we are able to mitigate most of the cache contention, but still
-    resulting some degree of jitter about 100us
+    these tuning techniques on Freesacle i.mx6 Sabre platform. Measurement results are shown in figure
+    \ref{fig:imx6_mctest_v}, \ref{fig:imx6_mctest_iso}, and \ref{fig:imx6_mctest_lock}, verifying the effectiveness of
+    these known tuning techniques and providing results as a baseline. We are able to see the WECT with and without
+    tuning are 100us and 100us. This gives us the hint that the scheduling would harms the real-time performance. This
+    scheduling overhead could be separated into 2 parts, scheduler overhead and cache contention on SMP system. With L2
+    Cache lockdown technique we are able to mitigate most of the cache contention, but still resulting some degree of
+    jitter about 100us
+
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-none.png} \caption{Mctest on i.mx6 Sabre}
+    \label{fig:imx6_mctest_v} \end{figure}
+
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-iso.png} \caption{Mctest on i.mx6 Sabre with
+    isolated cpu and tickless feature} \label{fig:imx6_mctest_iso} \end{figure}
+
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-lock.png} \caption{Mctest on i.mx6 Sabre with
+    isolated cpu, tickless feature and L2 cached lockdown} \label{fig:imx6_mctest_lock} \end{figure}
 
@@
 
-    In addition, we compared the user-space mctest result with kernel space measurement, shown in figure 6 and 7 with
-    WECT of 50us and 50us. With these result, we are able to identify the sources of jitter are system calls. To
-    mitigate these, we first proposed to rewrite real-time applications as kernel modules. But this is tedious and
-    making the debugging process difficult. Thus, we proposed a second approach, Kernel Mode Linux(KML) \cite{KML}
-    \cite{KMLConf}. KML enables the ability for specified user-space program running in kernel memory space. Thus,
-    system calls become jump instructions, not instruction trapping the processor. Also, this would mitigate the cache
-    contention while switching in and out the kernel during system call. In addition, we have also rewired system calls,
-    which have vDSO implementations \cite{vDSO}, to use vDSO implementation via KML. The result of user-space program
-    running in KML is shown in figure 8 with WECT of 20us, which proving the effectiveness of jitter mitigation from
-    KML.
+    In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
+    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WECT of 50us and 50us. With these result, we are
+    able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time
+    applications as kernel modules. But this is tedious and making the debugging process difficult. Thus, we proposed a
+    second approach, Kernel Mode Linux(KML) \cite{KML} \cite{KMLConf}. KML enables the ability for specified user-space
+    program running in kernel memory space. Thus, system calls become jump instructions, not instruction trapping the
+    processor. Also, this would mitigate the cache contention while switching in and out the kernel during system call.
+    In addition, we have also rewired system calls, which have vDSO implementations \cite{vDSO}, to use vDSO
+    implementation via KML. The result of user-space program running in KML is shown in figure \ref{fig:imx6_mctest_kml}
+    with WECT of 20us, which proving the effectiveness of jitter mitigation from KML.
+
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-k-none.png} \caption{Kernel mctest on i.mx6 Sabre}
+    \label{fig:imx6_mctest_k_v} \end{figure}
+
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-k-lock.png} \caption{Kernel mctest on i.mx6 Sabre
+    with isolated cpu, tickless feature and L2 cached lockdown} \label{fig:imx6_mctest_k_lock} \end{figure}
+
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-kml.png} \caption{Mctest on i.mx6 Sabre with
+    isolated cpu, tickless feature in KML} \label{fig:imx6_mctest_kml} \end{figure}
 
@@
     gives out the scheduler duration of a specified process, enabling us the understand the scheduling of real-time task
-    in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure 9.
-    The latency could be considered static with maximum 10us. This result matches traditional considerations, but with
-    the interference from other work-load, the jitter will start to emerge.
+    in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure
+    \ref{fig:sd_solo}. The latency could be considered static with maximum 10us. This result matches traditional
+    considerations, but with the interference from other work-load, the jitter will start to emerge.
+
+    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-solo.png} \caption{Scheduler duration of solo
+    cyclictest, no load} \label{fig:sd_solo} \end{figure}
 
@@
     condition, which has 3 stress threads, and a heavy loading condition, which has 8 stress threads. The result of mild
-    loading condition is shown in figure 10. This result also exhibits a mostly static scheduler duration with seldom
-    jitter with maximum of 20us. But putting the system in to heavy loading condition, the result, shown in figure 11
-    exhibits random jitter from 10us to 30us. The spread of distribution of scheduler duration, shown in figure 12,
-    would become wilder. This informs us that the scheduler duration is not a static value and will increase alone with
-    the system's load. Also informs that the scheduler duration contains but not only contains CFS algorithm task
-    selection process which is proved to be O(1).
+    loading condition is shown in figure \label{fig:sd_mild}. This result also exhibits a mostly static scheduler
+    duration with seldom jitter with maximum of 20us. But putting the system in to heavy loading condition, the result,
+    shown in figure \ref{fig:sd_heavy} exhibits random jitter from 10us to 30us. The spread of distribution of scheduler
+    duration, shown in figure \ref{fig:sd_heavy_d}, would become wilder. This informs us that the scheduler duration is
+    not a static value and will increase alone with the system's load. Also informs that the scheduler duration contains
+    but not only contains CFS algorithm task selection process which is proved to be O(1).
+
+    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-mild.png} \caption{Scheduler duration of cyclictest
+    with mild load} \label{fig:sd_mild} \end{figure}
+
+    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-heavy.png} \caption{Scheduler duration of cyclictest
+    with heavy load} \label{fig:sd_heavy} \end{figure}
+
+    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-heavy-d.png} \caption{Scheduler duration distribution
+    of cyclictest with heavy load} \label{fig:sd_heavy_d} \end{figure}
 
@@
     enter run-queue with short inter-arrival time against the cyclictest real-time thread, which was also being
-    waken-up. When this event happened, the scheduler duration will raise to 30us. This result, shown in figure 13 hints
-    us that not only long term overload system would exhibit large scheduler duration, but also short burst a
-    overloading condition during the real-time task scheduling and execution would cause the scheduler duration to
-    raise.
+    waken-up. When this event happened, the scheduler duration will raise to 30us. This result, shown in figure
+    \ref{fig:sd_mctest} hints us that not only long term overload system would exhibit large scheduler duration, but
+    also short burst a overloading condition during the real-time task scheduling and execution would cause the
+    scheduler duration to raise.
+
+    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-mctest.png} \caption{Scheduler duration of cyclictest
+    with short inter-arrival time to run-queue against other task} \label{fig:sd_mctest} \end{figure}
 

### 2017-03-25 paper.tex
adjust sd-heavy-d image size

@@
 
-    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-heavy-d.png} \caption{Scheduler duration distribution
+    \begin{figure} \centering \includegraphics[width=3in]{img/sd-heavy-d.png} \caption{Scheduler duration distribution
     of cyclictest with heavy load} \label{fig:sd_heavy_d} \end{figure}

### 2017-03-25 paper.tex
Update the numbers

@@
     these known tuning techniques and providing results as a baseline. We are able to see the WECT with and without
-    tuning are 100us and 100us. This gives us the hint that the scheduling would harms the real-time performance. This
+    tuning are 153us and 86us. This gives us the hint that the scheduling would harms the real-time performance. This
     scheduling overhead could be separated into 2 parts, scheduler overhead and cache contention on SMP system. With L2
     Cache lockdown technique we are able to mitigate most of the cache contention, but still resulting some degree of
-    jitter about 100us
+    jitter about 76us in maximum.
 
@@
     In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
-    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WECT of 50us and 50us. With these result, we are
+    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WECT of 27us and 17us. With these result, we are
     able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time
@@
     implementation via KML. The result of user-space program running in KML is shown in figure \ref{fig:imx6_mctest_kml}
-    with WECT of 20us, which proving the effectiveness of jitter mitigation from KML.
+    with WECT of 27us (excluding initialization jitter), which proving the effectiveness of jitter mitigation from KML.
 
@@
     in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure
-    \ref{fig:sd_solo}. The latency could be considered static with maximum 10us. This result matches traditional
+    \ref{fig:sd_solo}. The latency could be considered static with maximum 17us. This result matches traditional
     considerations, but with the interference from other work-load, the jitter will start to emerge.
@@
     duration with seldom jitter with maximum of 20us. But putting the system in to heavy loading condition, the result,
-    shown in figure \ref{fig:sd_heavy} exhibits random jitter from 10us to 30us. The spread of distribution of scheduler
+    shown in figure \ref{fig:sd_heavy} exhibits random jitter up to 34us. The spread of distribution of scheduler
     duration, shown in figure \ref{fig:sd_heavy_d}, would become wilder. This informs us that the scheduler duration is
@@
     enter run-queue with short inter-arrival time against the cyclictest real-time thread, which was also being
-    waken-up. When this event happened, the scheduler duration will raise to 30us. This result, shown in figure
-    \ref{fig:sd_mctest} hints us that not only long term overload system would exhibit large scheduler duration, but
-    also short burst a overloading condition during the real-time task scheduling and execution would cause the
+    waken-up. When this event happened, the scheduler duration will raise to maximum of 23us. This result, shown in
+    figure \ref{fig:sd_mctest} hints us that not only long term overload system would exhibit large scheduler duration,
+    but also short burst a overloading condition during the real-time task scheduling and execution would cause the
     scheduler duration to raise.

### 2017-04-09 paper.tex
Preliminary descriptions

@@
 \section{Introduction}
+
+The processing of time-critical tasks, depends upon the capacity of the system to respondto an event, within
+a known and bounded interval of time.
+
+Existing techniques for effectively scheduling real-time workloads on multiprocessors has been increasing recently.
+Two factors are driving this movement. First, algorithmic research on this topic has resulted in a number of new
+scheduling approaches that remove some of the fundamental barriers imposed by partitioning approaches, the scheme
+smost commonly considered in earlier work. Second, the landscape in terms of hardware platforms has been changing:
+"server-class" multiprocessor machines have been availablefor some time now, and SoC vendors are shifting to
+multi-core technologies as a solution to the "thermal roadblock" imposed by single-core designs. In multicore
+platforms, several processor cores are placed on a single chip. Most major chip manufacturers currently offer
+more core.
 
@@
     in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure
-    \ref{fig:sd_solo}. The latency could be considered static with maximum 17us. This result matches traditional
+    \ref{fig:sd_noload}. The latency could be considered static with maximum 17us. This result matches traditional
     considerations, but with the interference from other work-load, the jitter will start to emerge.
 
-    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-solo.png} \caption{Scheduler duration of solo
-    cyclictest, no load} \label{fig:sd_solo} \end{figure}
+    \begin{figure} \centering \includegraphics[width=3in]{img/sd-noload.png} \caption{Scheduler duration of solo
+    cyclictest, no load} \label{fig:sd_noload} \end{figure}
 
-\subsubsection{Overloaded System}
+\subsubsection{Scheduler Duration under Different Loading Condition}
 
-    We created additional work-load, executing alone with cyclictest during profiling session. We created a mild loading
-    condition, which has 3 stress threads, and a heavy loading condition, which has 8 stress threads. The result of mild
-    loading condition is shown in figure \label{fig:sd_mild}. This result also exhibits a mostly static scheduler
-    duration with seldom jitter with maximum of 20us. But putting the system in to heavy loading condition, the result,
-    shown in figure \ref{fig:sd_heavy} exhibits random jitter up to 34us. The spread of distribution of scheduler
-    duration, shown in figure \ref{fig:sd_heavy_d}, would become wilder. This informs us that the scheduler duration is
-    not a static value and will increase alone with the system's load. Also informs that the scheduler duration contains
-    but not only contains CFS algorithm task selection process which is proved to be O(1).
+    To measure the source of scheduler duration jitter, We created additional work-load, executing alone with
+    cyclictest, schedulered with schedFIFO with highest priority in SoCFPGA based system, during profiling session. We
+    created a overloaded condition, which has 8 stress threads, doing either CPU, memory or I/O bounded task. The
+    scheduler duration of cyclictest real-time task under each type of loading condition is shown in figure
+    \ref{fig:sd_cpu}, \ref{fig:sd_memory}, and \ref{fig:sd_io}. This result exhibits a mostly static scheduler
+    duration with seldom jitter with maximum of 20us in CPU and I/O bounded loads. But putting the system in to heavy
+    memory loading condition, the result, shown in figure \ref{fig:sd_memory} shows an increased average of scheduler
+    duration and exhibits random jitter up to 34us. The spread of distribution of scheduler duration would also become
+    wilder. This informs us that the scheduler duration is not a static value and will increase alone with the system's
+    load, especially memory related load. This informs that the scheduler runnable task selection process execution time
+    could be lengthen by user-space task, doing memory bounded tasks.
 
-    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-mild.png} \caption{Scheduler duration of cyclictest
-    with mild load} \label{fig:sd_mild} \end{figure}
+    \begin{figure} \centering \includegraphics[width=3in]{img/sd-cpu.png} \caption{Scheduler duration of cyclictest
+    with CPU bounded load} \label{fig:sd_cpu} \end{figure}
 
-    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-heavy.png} \caption{Scheduler duration of cyclictest
-    with heavy load} \label{fig:sd_heavy} \end{figure}
+    \begin{figure} \centering \includegraphics[width=3in]{img/sd-memory.png} \caption{Scheduler duration of cyclictest
+    with memory bounded load} \label{fig:sd_memory} \end{figure}
 
-    \begin{figure} \centering \includegraphics[width=3in]{img/sd-heavy-d.png} \caption{Scheduler duration distribution
-    of cyclictest with heavy load} \label{fig:sd_heavy_d} \end{figure}
+    \begin{figure} \centering \includegraphics[width=3in]{img/sd-io.png} \caption{Scheduler duration distribution of
+    cyclictest with I/O bounded load} \label{fig:sd_io} \end{figure}
 
-\subsubsection{Short Inter-Arrival Time}
+    To mitigate the influence of memory bounded tasks, we isolated the real-time task into dedicated CPU core, and
+    pinned memory bounded tasks to another CPU core. In addition, we make the shared L2 cache only accessible from the
+    CPU core, running real-time task. The result of scheduler duration in shown in figure \ref{fig:sd_iso}. The
+    scheduler duration is stabilized and showing as distribution as other loading conditions. The stress memory bounded
+    tasks were designed to spin on malloc and free calls. This suggests us that memory allocation and deallocation would
+    decrease the scheduler performance and increase its execution jitter via cache and memory model. Also, we gathered
+    the result of pining both real-time and loads to same CPU core. Figure \ref{fig:sd_same_no_cache} shows the result
+    of running on CPU core without L2 cache.  Comparing with figure \ref{fig:sd_memory}, result under 2 core SMP, this
+    result showns a slight improvement of average latency and jitter. This informs that shared L2 cache and dynamic
+    number of loading tasks, sharing CPU with real-time task, would be the source of scheduler duration jitter. Thus,
+    decrease the use of dynamic memory allocation, real-time task CPU isolation and cache lockdown could prevent raising
+    the scheduler duration, keeping it as a stable value, about 10us.
 
-    We also captured large jitter of scheduler duration on a mild loaded system. The experiment is running mctest with
-    cyclictest. We pinned kernel module mctest to use first processor, causing cyclictest real-time thread and main
-    thread being scheduler onto second processor. On most of the time, this execution schema results the same result as
-    cyclictest executing solely in the system. But on some occasions, the cyclictest main thread would be waken-up and
-    enter run-queue with short inter-arrival time against the cyclictest real-time thread, which was also being
-    waken-up. When this event happened, the scheduler duration will raise to maximum of 23us. This result, shown in
-    figure \ref{fig:sd_mctest} hints us that not only long term overload system would exhibit large scheduler duration,
-    but also short burst a overloading condition during the real-time task scheduling and execution would cause the
-    scheduler duration to raise.
+    \begin{figure} \centering \includegraphics[width=3in]{img/sd-iso.png} \caption{Scheduler duration of cyclictest with
+    memory bounded load on different cores} \label{fig:sd_iso} \end{figure}
 
-    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-mctest.png} \caption{Scheduler duration of cyclictest
-    with short inter-arrival time to run-queue against other task} \label{fig:sd_mctest} \end{figure}
+    \begin{figure} \centering \includegraphics[width=3in]{img/sd-same-no-cache.png} \caption{Scheduler duration of
+    cyclictest with memory bounded load on same core} \label{fig:sd_same_no_cache} \end{figure}
 

### 2017-04-10 paper.tex
Fix typo

@@
     interrupt execution, scheduling events, etc. on per processor core basis. This methodology method differs from
-    profiling based methodology tools, e.g. perf \cite{perf}, lacking high fidelity, all-recorded profiling result of
+    profiling based methodology tools, e.g. perf \cite{perf}, lacking of high fidelity, all-recorded profiling result of
     the target system. Our proposed tool can do full-detailed record in microsecond scale on x86-64 and ARM system,
@@
     being used in a wide field of applications. These systems are running buildroot \cite{buildroot} built Linux with
-    kernel version 4.4 and PR\textunderscore RT \cite{preemptrt} patches.
+    kernel version 4.4 and PREEMPT\textunderscore RT \cite{preemptrt} patches.
 

### 2017-04-19 paper.tex
Revise the scheduler duration experiment and result

--- 2017-04-09 paper.tex
@@
 \section{Introduction}
-
-The processing of time-critical tasks, depends upon the capacity of the system to respondto an event, within
-a known and bounded interval of time.
-
-Existing techniques for effectively scheduling real-time workloads on multiprocessors has been increasing recently.
-Two factors are driving this movement. First, algorithmic research on this topic has resulted in a number of new
-scheduling approaches that remove some of the fundamental barriers imposed by partitioning approaches, the scheme
-smost commonly considered in earlier work. Second, the landscape in terms of hardware platforms has been changing:
-"server-class" multiprocessor machines have been availablefor some time now, and SoC vendors are shifting to
-multi-core technologies as a solution to the "thermal roadblock" imposed by single-core designs. In multicore
-platforms, several processor cores are placed on a single chip. Most major chip manufacturers currently offer
-more core.
 

### 2017-04-21 paper.tex
Cite LITMUS^RT

--- 2017-04-10 paper.tex
@@
 \section{Related Work}
+
+LITMUS\textsuperscript{RT} \cite{LITMUS} is an open source effort for empirically evaluating multiprocessor
+real-time scheduling algorithms implemented with Linux. The tested algorithms were compared based on both
+raw performance and schedulability (with real overheads considered) assuming either hard or soft real-time
+constraints.
 

### 2017-04-21 paper.tex
Mention PREEMPT-RT

@@
 
+It has been more than 10 years since Linux engineers collaborate on the in-kernel real-time development, real-time
+preemption or PREEMPT\textunderscore RT \cite{rt-linux}. The preemption latency of Linux kernel has been reduced by
+one to several orders of magnitude, allowing it to compete commercial real-time operating systems.
+
 LITMUS\textsuperscript{RT} \cite{LITMUS} is an open source effort for empirically evaluating multiprocessor
@@
 
+Another relevant Linux-related prior effort is work by Calandrino \textit{et al}. \cite{Lozi:2016:LSD:2901318.2901326},
+who built new tools that check for violation of the invariant online and visualize scheduling activity while analyzing
+performance degradation for synchronization-heavy application on Linux.
+
 \section{Methodology}
 
-    Based on the works presented above, we have methods to measure the overall wake-up latency and context-switch
-    latency, using cyclictest and lmbench. Also, it's able to show that the CFS algorithm has O(1) complexity on
-    selecting next task, giving static latency. Thus, overall  and parts of latency of a Linux system can be determined,
-    but the measurement methodology and tool of scheduler latency, shown in figure \ref{fig:latency_timeline}, are
-    lacking. Therefore, we developed a evaluation tool of scheduler duration jitter, based on methodology method of A
-    Decade of Wasted Cores \cite{Lozi:2016:LSD:2901318.2901326}. This methodology method enabled us to record the
-    scheduler states including, executing process ID (PID), PID in scheduler run-queue, context switch points, timer
-    interrupt execution, scheduling events, etc. on per processor core basis. This methodology method differs from
-    profiling based methodology tools, e.g. perf \cite{perf}, lacking of high fidelity, all-recorded profiling result of
-    the target system. Our proposed tool can do full-detailed record in microsecond scale on x86-64 and ARM system,
-    which is able to capture the impact to real-time performance of occasional short-burst scheduler events, which only
-    last less that 10us. These events are mostly not shown in the result of sampling based measurement which focus on
-    average-case execution time(ACET). By analyzing full-detailed record, we are able to not only capture the worst-case
-    execution time (WCET), but also understand the cause of these incidents.
+    The Completely Fair Scheduler (CFS) is a process scheduler which was merged into the 2.6.23 release of Linux kernel
+    and is the default scheduler with O(1) complexity on selecting next task, giving static latency. In other words, parts
+    of latency source of a Linux-based real-time system can be determined, at least for scheduler duration, shown in
+    Figure \ref{fig:latency_timeline}.
 
-    In addition, the behavior and loading characteristic of typical work-load used during test in above works, e.g.
+    A new tool to visualize scheduling visualize is developed, enabling developers to record the scheduler states
+    including executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution,
+    scheduling events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g.
+    perf \cite{perf}, by means of high fidelity and full-profiling fashion of the target system. Our proposed tool can
+    gather entire activities inside Linux kernel in microsecond scale on both x86-64 and ARM system, being able to capture
+    the impact to real-time performance of occasional short-burst scheduler events, which only last less that 10us.
+    These events are mostly not shown in the result of sampling based measurement which focus on average-case execution
+    time(ACET). By analyzing full-detailed record, we are able to not only capture the worst-case execution time (WCET),
+    but also understand the cause of these incidents.
+
+    Moreover, the behavior and loading characteristic of typical work-load used during test in above works, e.g.
     hackbench, stress \cite{rt-tests}, etc. are far from the real-world real-time applications. These problems not only
@@
 
-    In aid of these developed tools and work presented above, we did multiple experiments and measurement of 2 ARM
-    Cortex-A9 based platform, shown in table I. These platforms are selected as CMP based ARM system are emerging and
-    being used in a wide field of applications. These systems are running buildroot \cite{buildroot} built Linux with
-    kernel version 4.4 and PREEMPT\textunderscore RT \cite{preemptrt} patches.
+    In aid of these developed tools and work presented above, 
+    We performed multiple experiments on 2 ARM Cortex-A9 based boards, shown in table I, widely adopted by industrial
+    automation applications. Each test runs Linux kernel version 4.4 and PREEMPT\textunderscore RT \cite{preemptrt} with
+    minimal root file system generated by buildroot \cite{buildroot}.
 
     \begin{table*}[] \centering \caption{Experiment Platforms} \begin{tabular}{|l|c|c|} \hline Platform Name & Altera
-        SoC FPGA Development Kit & Freescale i.mx6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
+        SoC-FPGA Development Kit & NXP i.MX6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
         \hline Memory & 1 GB & 1 GB \\ \hline Additional configuration & None & \begin{tabular}[c]{@{}c@{}}L2 Cache
@@
     \ref{fig:imx6_mctest_v}, \ref{fig:imx6_mctest_iso}, and \ref{fig:imx6_mctest_lock}, verifying the effectiveness of
-    these known tuning techniques and providing results as a baseline. We are able to see the WECT with and without
+    these known tuning techniques and providing results as a baseline. We are able to see the WCET with and without
     tuning are 153us and 86us. This gives us the hint that the scheduling would harms the real-time performance. This
@@
     In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
-    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WECT of 27us and 17us. With these result, we are
+    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WCET of 27us and 17us. With these result, we are
     able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time
@@
     implementation via KML. The result of user-space program running in KML is shown in figure \ref{fig:imx6_mctest_kml}
-    with WECT of 27us (excluding initialization jitter), which proving the effectiveness of jitter mitigation from KML.
+    with WCET of 27us (excluding initialization jitter), which proving the effectiveness of jitter mitigation from KML.
 
@@
     gives out the scheduler duration of a specified process, enabling us the understand the scheduling of real-time task
-    in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure
+    in SMP system. The result of running a solo instance of cyclictest on SoC-FPGA Development Kit is shown in figure
     \ref{fig:sd_noload}. The latency could be considered static with maximum 17us. This result matches traditional
@@
     To measure the source of scheduler duration jitter, We created additional work-load, executing alone with
-    cyclictest, schedulered with schedFIFO with highest priority in SoCFPGA based system, during profiling session. We
+    cyclictest, schedulered with schedFIFO with highest priority in SoC-FPGA based system, during profiling session. We
     created a overloaded condition, which has 8 stress threads, doing either CPU, memory or I/O bounded task. The

### 2017-04-21 paper.tex
Remove LITMUS^RT to simply

@@
 
-The processing of time-critical tasks, depends upon the capacity of the system to respondto an event, within
-a known and bounded interval of time.
+The processing of time-critical tasks, depends upon the capacity of the system to respond to an event, within
+a known and bounded interval of time. Existing techniques for effectively scheduling real-time workloads on
+multiprocessors has been increasing recently.
 
-Existing techniques for effectively scheduling real-time workloads on multiprocessors has been increasing recently.
 Two factors are driving this movement. First, algorithmic research on this topic has resulted in a number of new
@@
 one to several orders of magnitude, allowing it to compete commercial real-time operating systems.
-
-LITMUS\textsuperscript{RT} \cite{LITMUS} is an open source effort for empirically evaluating multiprocessor
-real-time scheduling algorithms implemented with Linux. The tested algorithms were compared based on both
-raw performance and schedulability (with real overheads considered) assuming either hard or soft real-time
-constraints.
 
@@
     scheduling events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g.
-    perf \cite{perf}, by means of high fidelity and full-profiling fashion of the target system. Our proposed tool can
-    gather entire activities inside Linux kernel in microsecond scale on both x86-64 and ARM system, being able to capture
-    the impact to real-time performance of occasional short-burst scheduler events, which only last less that 10us.
-    These events are mostly not shown in the result of sampling based measurement which focus on average-case execution
-    time(ACET). By analyzing full-detailed record, we are able to not only capture the worst-case execution time (WCET),
-    but also understand the cause of these incidents.
+    perf \cite{perf}, by means of high fidelity and full-profiling fashion of the target system. It gathers entire
+    activities inside Linux kernel in microsecond scale, being able to capture the impact of occasional short-burst
+    scheduler events, which only last less that 10us. These events are mostly not shown in the result of sampling based
+    measurement which focus on average-case execution time. By analyzing full-detailed record, we can not only
+    capture the worst-case execution time (WCET), but also understand the cause of these incidents.
 
-    Moreover, the behavior and loading characteristic of typical work-load used during test in above works, e.g.
-    hackbench, stress \cite{rt-tests}, etc. are far from the real-world real-time applications. These problems not only
-    would reduce the significant of target system jitter measurement, but also will make incidents, harming the
-    real-time performance, obscure. In result of this frustration, we also created a testing framework hosing an
-    algorithm which resembled a real-time robot control system execution behavior, named mctest. This work-load
-    application has the ability to be compiled either as user-space program or kernel module, provides observation of
-    the characteristic of target application execution in both user-space and kernel-space. This would gives the insight
-    of system-call and user-space I/O overhead, which does not exist in kernel module. In addition, mctest would do a
-    series of identically executions and record the execution time of each turn. These records can be used to determined
-    the execution jitter of the application on the real-time system, which besides wakeup latency. This could be used to
-    reflect to the system-call overhead of the system. We have been utilizing mctest as the testing work-load and jitter
-    measurement tool during methodology.
+    Moreover, the behavior and characteristic of typical work-load used in the past, such as hackbench and stress \cite{rt-tests},
+    are far from the real-world real-time applications. In result of this frustration, we also created a testing framework
+    hosting a set of algorithms which resembled a real-time robot control system execution behavior, named after "mctest".
+    It has the ability to be compiled either as user-space program or kernel module, that would give the insight of system-call
+    and user-space I/O overhead, which is eliminated in kernel module expectedly.
+
+    In addition, mctest would do a series of identically executions and record the execution time of each turn. These records
+    can be used to determined the execution jitter of the application on the real-time system, which besides wakeup latency.
+    This could be used to reflect to the system-call overhead of the system. We have been utilizing mctest as the testing
+    work-load and jitter measurement tool during methodology.
 
@@
 
-    In aid of these developed tools and work presented above, 
-    We performed multiple experiments on 2 ARM Cortex-A9 based boards, shown in table I, widely adopted by industrial
+    We performed multiple experiments on 2 ARM Cortex-A9 based boards, shown in Table \ref{hardware_list}, widely adopted by industrial
     automation applications. Each test runs Linux kernel version 4.4 and PREEMPT\textunderscore RT \cite{preemptrt} with
-    minimal root file system generated by buildroot \cite{buildroot}.
+    minimal root file system.
 
-    \begin{table*}[] \centering \caption{Experiment Platforms} \begin{tabular}{|l|c|c|} \hline Platform Name & Altera
-        SoC-FPGA Development Kit & NXP i.MX6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
+    \begin{table*}[]
+        \centering \caption{Experiment Platforms}
+        \label{hardware_list}
+	\begin{tabular}{|l|c|c|} \hline Platform Name & Altera
+        Cyclone V Development Kit & NXP i.MX6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
         \hline Memory & 1 GB & 1 GB \\ \hline Additional configuration & None & \begin{tabular}[c]{@{}c@{}}L2 Cache
@@
     feature of kernel \cite{tickless}, L2 cache lockdown. We compared the measurement result of mctest with and without
-    these tuning techniques on Freesacle i.mx6 Sabre platform. Measurement results are shown in figure
-    \ref{fig:imx6_mctest_v}, \ref{fig:imx6_mctest_iso}, and \ref{fig:imx6_mctest_lock}, verifying the effectiveness of
+    these tuning techniques on NXP i.MX6 Sabre platform. Measurement results are shown in
+    Figure \ref{fig:imx6_mctest_v}, \ref{fig:imx6_mctest_iso}, and \ref{fig:imx6_mctest_lock}, verifying the effectiveness of
     these known tuning techniques and providing results as a baseline. We are able to see the WCET with and without
@@
     scheduling overhead could be separated into 2 parts, scheduler overhead and cache contention on SMP system. With L2
-    Cache lockdown technique we are able to mitigate most of the cache contention, but still resulting some degree of
-    jitter about 76us in maximum.
+    Cache lockdown we are able to mitigate most of the cache contention, but still resulting some degree of jitter about
+    76us in maximum.
 
-    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-none.png} \caption{Mctest on i.mx6 Sabre}
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-none.png} \caption{Mctest on i.MX6 Sabre}
     \label{fig:imx6_mctest_v} \end{figure}
 
-    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-iso.png} \caption{Mctest on i.mx6 Sabre with
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-iso.png} \caption{Mctest on i.MX6 Sabre with
     isolated cpu and tickless feature} \label{fig:imx6_mctest_iso} \end{figure}
 
-    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-lock.png} \caption{Mctest on i.mx6 Sabre with
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-lock.png} \caption{Mctest on i.MX6 Sabre with
     isolated cpu, tickless feature and L2 cached lockdown} \label{fig:imx6_mctest_lock} \end{figure}
 
-\subsection{System Call Overhead and Kernel Mode Linux}
+    \subsection{Eliminate System Call Overhead}
 
@@
     applications as kernel modules. But this is tedious and making the debugging process difficult. Thus, we proposed a
-    second approach, Kernel Mode Linux(KML) \cite{KML} \cite{KMLConf}. KML enables the ability for specified user-space
-    program running in kernel memory space. Thus, system calls become jump instructions, not instruction trapping the
-    processor. Also, this would mitigate the cache contention while switching in and out the kernel during system call.
-    In addition, we have also rewired system calls, which have vDSO implementations \cite{vDSO}, to use vDSO
-    implementation via KML. The result of user-space program running in KML is shown in figure \ref{fig:imx6_mctest_kml}
-    with WCET of 27us (excluding initialization jitter), which proving the effectiveness of jitter mitigation from KML.
+    second approach, Kernel Mode Linux(KML) \cite{KML} \cite{KMLConf}, allowing userspace programs running in kernel
+    address space. Thus, system calls become jump instructions instead of instructions that traps the processor. Also,
+    this would mitigate the cache contention while switching in and out the kernel during system call.
+    In addition, we have wrapped system calls with vDSO \cite{vDSO} for better compatibility. It results in
+    user-space program running in KML with WCET similar to Linux kernel module variants.
 
-    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-k-none.png} \caption{Kernel mctest on i.mx6 Sabre}
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-k-none.png} \caption{Kernel mctest on i.MX6 Sabre}
     \label{fig:imx6_mctest_k_v} \end{figure}
 
-    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-k-lock.png} \caption{Kernel mctest on i.mx6 Sabre
+    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-k-lock.png} \caption{Kernel mctest on i.MX6 Sabre
     with isolated cpu, tickless feature and L2 cached lockdown} \label{fig:imx6_mctest_k_lock} \end{figure}
-
-    \begin{figure} \centering \includegraphics[width=3in]{img/mctest-kml.png} \caption{Mctest on i.mx6 Sabre with
-    isolated cpu, tickless feature in KML} \label{fig:imx6_mctest_kml} \end{figure}
 
@@
     context-switching latency, we would like to evaluate the scheduler duration. Traditionally, the latency of this part
-    is considered static with the CFS algorithm complexity, designed to be O(1), but real measurement result are
+    is considered static with the CFS algorithm complexity, designed to be O(1), but real measurement results are
     lacking. Thus, we set our proposed profiler to record the increment of scheduler run-queue and scheduler
@@
     gives out the scheduler duration of a specified process, enabling us the understand the scheduling of real-time task
-    in SMP system. The result of running a solo instance of cyclictest on SoC-FPGA Development Kit is shown in figure
+    in SMP system. The result of running a solo instance of cyclictest on Cyclone V Development Kit is shown in figure
     \ref{fig:sd_noload}. The latency could be considered static with maximum 17us. This result matches traditional
@@
     To measure the source of scheduler duration jitter, We created additional work-load, executing alone with
-    cyclictest, schedulered with schedFIFO with highest priority in SoC-FPGA based system, during profiling session. We
+    cyclictest, with FIFO scheduling policy and highest priority in Cyclone V based system, during profiling session. We
     created a overloaded condition, which has 8 stress threads, doing either CPU, memory or I/O bounded task. The

### 2017-04-21 paper.tex
Ready to submit

@@
 
-\title{Title}
+\title{An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling}
 
 \author{\IEEEauthorblockN{Ching-Chun (Jim) Huang} \IEEEauthorblockA{Department of\\Computer Science and Information
-Engineering\\National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\ Email:
-jserv@ccns.ncku.edu.tw} \and \IEEEauthorblockN{Chung-Fan Yang} \IEEEauthorblockA{Department of Electrical Engineering\\
-National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\ Email:
-E24026048@mail.ncku.edu.tw}}
+Engineering\\National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
+\and \IEEEauthorblockN{Chung-Fan Yang} \IEEEauthorblockA{Department of Electrical Engineering\\
+National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}}
 
@@
 \begin{abstract}
+A real-time, Linux-based testbed, which we have developed for empirically evaluating multiprocessor
+scheduling hehavior is presented, along with various enhancements that remove some of the fundamental
+barriers to eliminate potential latency. Both raw performance and schedulability are considered for
+hard real-time constraints. To our knowledge, this paper is the first attempt by anyone to obtain
+comprehensive performance results regarding the scheduler and its interaction with external events.
 \end{abstract}
@@
 The processing of time-critical tasks, depends upon the capacity of the system to respond to an event, within
-a known and bounded interval of time. Existing techniques for effectively scheduling real-time workloads on
-multiprocessors has been increasing recently.
+a known and bounded interval of time. We have constructed a set of system utilities as a testbed to discover
+Linux scheduling, multi-core overhead and real-time performance from microscopic view.
 
-Two factors are driving this movement. First, algorithmic research on this topic has resulted in a number of new
-scheduling approaches that remove some of the fundamental barriers imposed by partitioning approaches, the scheme
-smost commonly considered in earlier work. Second, the landscape in terms of hardware platforms has been changing:
-"server-class" multiprocessor machines have been availablefor some time now, and SoC vendors are shifting to
-multi-core technologies as a solution to the "thermal roadblock" imposed by single-core designs. In multicore
-platforms, several processor cores are placed on a single chip. Most major chip manufacturers currently offer
-more core.
+The landscape in terms of hardware platforms has been changing: "server-class" multiprocessor machines have
+been available for some time now, and SoC vendors are shifting to multi-core technologies as real-time system
+solutions. Our goal was to produce a platform that supports both static and dynamic workloads for real-time constraints.
 
@@
 \section{Conclusion}
-
-    We have evaluated the real-time behavior of Linux by profiling kernel scheduler and measuring the latency of various
-    kernel variants. An intensive interrupt load can cause long OS latencies due to the design of the interrupt
+    We have evaluated Linux real-time behavior by profiling kernel scheduler and measuring the latency.
+    An intensive interrupt load can cause long OS latencies due to the design of the interrupt
     processing mechanism. We proposed new tools to visualize task scheduling in fine-grained scale(microsecond level).
-    This enabled us not only focusing on interrupt latency, but also scheduler durations, lock, and etc. It would thus
-    be highly desirable to combine existing techniques, e.g KML, isolated CPU, tickless kernel, to improve task
-    responsiveness under various target application characteristics, on top of PREEMPT\textunderscore RT.
+    It encourages us to focus on not only interrupt latency but also scheduler durations, lock, etc., andt would thus
+    be highly desirable to combine existing techniques, e.g isolated CPU, tickless kernel, to improve task responsiveness
+    under various target application characteristics, with our testbed.
 

### 2017-04-21 paper.tex
Fix typo

@@
 A real-time, Linux-based testbed, which we have developed for empirically evaluating multiprocessor
-scheduling hehavior is presented, along with various enhancements that remove some of the fundamental
+scheduling behavior is presented, along with various enhancements that remove some of the fundamental
 barriers to eliminate potential latency. Both raw performance and schedulability are considered for

### 2017-05-10 paper.tex
Fix grammar errors

@@
 
-    A new tool to visualize scheduling visualize is developed, enabling developers to record the scheduler states
+    A new tool to visualize scheduling is developed, enabling developers to record the scheduler states
     including executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution,
@@
     In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
-    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WCET of 27us and 17us. With these result, we are
+    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WCET of 27us and 17us. With these results, we are
     able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time

### 2017-05-14 paper.tex
Add benchmarking and profiling process and parameter

@@
 
-    A new tool to visualize scheduling is developed, enabling developers to record the scheduler states
-    including executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution,
-    scheduling events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g.
-    perf \cite{perf}, by means of high fidelity and full-profiling fashion of the target system. It gathers entire
-    activities inside Linux kernel in microsecond scale, being able to capture the impact of occasional short-burst
-    scheduler events, which only last less that 10us. These events are mostly not shown in the result of sampling based
-    measurement which focus on average-case execution time. By analyzing full-detailed record, we can not only
-    capture the worst-case execution time (WCET), but also understand the cause of these incidents.
+    A new tool to visualize scheduling is developed, enabling developers to record the scheduler states including
+    executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution, scheduling
+    events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g. perf \cite{perf},
+    by means of high fidelity and full-profiling fashion of the target system. It gathers entire activities inside Linux
+    kernel in microsecond scale, being able to capture the impact of occasional short-burst scheduler events, which only
+    last less that 10us. These events are mostly not shown in the result of sampling based measurement which focus on
+    average-case execution time. By analyzing full-detailed record, we can not only capture the worst-case execution
+    time (WCET), but also understand the cause of these incidents. This scheduler benchmarking process is composed of
+    starting a benchmark, cyclictest, and profiler in the same time. Cyclictest were set with "-mnq
+    -p 90 --policy=fifo -h 1000 -i 1000 -l 10000." The profiling last 3 seconds. Logs are extracted from the profiler
+    and analyzed afterward.
 
@@
 
-    In addition, mctest would do a series of identically executions and record the execution time of each turn. These records
-    can be used to determined the execution jitter of the application on the real-time system, which besides wakeup latency.
-    This could be used to reflect to the system-call overhead of the system. We have been utilizing mctest as the testing
-    work-load and jitter measurement tool during methodology.
-
-    \begin{figure} \centering \includegraphics[width=3.5in]{img/latency_timeline.png} \caption{Task Wake-up Latency}
+    \begin{figure} \centering \includegraphics[width=3.3in]{img/latency_timeline.png} \caption{Task Wake-up Latency}
     \label{fig:latency_timeline} \end{figure}
@@
     \begin{figure} \centering \includegraphics[width=3in]{img/sd-cpu.png} \caption{Scheduler duration of cyclictest
-    with CPU bounded load} \label{fig:sd_cpu} \end{figure}
+    with CPU bounded load (stress with 8 cpu threads)} \label{fig:sd_cpu} \end{figure}
 
     \begin{figure} \centering \includegraphics[width=3in]{img/sd-memory.png} \caption{Scheduler duration of cyclictest
-    with memory bounded load} \label{fig:sd_memory} \end{figure}
+    with memory bounded load (stress with 8 vm threads, vm work size=16M)} \label{fig:sd_memory} \end{figure}
 
     \begin{figure} \centering \includegraphics[width=3in]{img/sd-io.png} \caption{Scheduler duration distribution of
-    cyclictest with I/O bounded load} \label{fig:sd_io} \end{figure}
+    cyclictest with I/O bounded load (stress with 8 io threads)} \label{fig:sd_io} \end{figure}
 
@@
     \begin{figure} \centering \includegraphics[width=3in]{img/sd-iso.png} \caption{Scheduler duration of cyclictest with
-    memory bounded load on different cores} \label{fig:sd_iso} \end{figure}
+    memory bounded load (stress with 8 vm threads, vm work size=16M) on different cores} \label{fig:sd_iso} \end{figure}
 
     \begin{figure} \centering \includegraphics[width=3in]{img/sd-same-no-cache.png} \caption{Scheduler duration of
-    cyclictest with memory bounded load on same core} \label{fig:sd_same_no_cache} \end{figure}
+    cyclictest with memory bounded load (stress with 8 vm threads, vm work size=16M) on same core} \label{fig:sd_same_no_cache} \end{figure}
 

### 2017-05-15 paper.tex
Fix typo: L2 cache lockdown

@@
         Cyclone V Development Kit & NXP i.MX6 Sabre \\ \hline Processor & 2x ARM Cortex-A9 & 4x ARM Cortex-A9 \\
-        \hline Memory & 1 GB & 1 GB \\ \hline Additional configuration & None & \begin{tabular}[c]{@{}c@{}}L2 Cache
-        locked down to CPU1,\\ Isolated CPU1,\\ Enabled tickless on CPU1 \\ Real-time task pinned to CPU1 \end{tabular}
+        \hline Memory & 1 GB & 1 GB \\ \hline Additional configuration & None & \begin{tabular}[c]{@{}c@{}}L2 Cache lockdown on isolated CPU1,\\ Enabled tickless on CPU1 \\ Real-time task pinned to CPU1 \end{tabular}
     \\ \hline \end{tabular} \end{table*}

### 2017-05-15 paper.tex
Wording tweaks

@@
     memory loading condition, the result, shown in figure \ref{fig:sd_memory} shows an increased average of scheduler
-    duration and exhibits random jitter up to 34us. The spread of distribution of scheduler duration would also become
-    wilder. This informs us that the scheduler duration is not a static value and will increase alone with the system's
-    load, especially memory related load. This informs that the scheduler runnable task selection process execution time
+    duration and exhibits random jitter up to 34us.
+The spread of distribution of scheduler duration would also become wilder, that implies scheduler duration is not a static value and will increase alone with the system load, especially memory related load.
+    Therefore, the scheduler runnable task selection process execution time
     could be lengthen by user-space task, doing memory bounded tasks.
@@
     decrease the scheduler performance and increase its execution jitter via cache and memory model. Also, we gathered
-    the result of pining both real-time and loads to same CPU core. Figure \ref{fig:sd_same_no_cache} shows the result
+    the result of pining both real-time and loads to same CPU core.
+
+    Figure \ref{fig:sd_same_no_cache} shows the result
     of running on CPU core without L2 cache.  Comparing with figure \ref{fig:sd_memory}, result under 2 core SMP, this
-    result showns a slight improvement of average latency and jitter. This informs that shared L2 cache and dynamic
+    result showns a slight improvement of average latency and jitter, that means shared L2 cache and dynamic
     number of loading tasks, sharing CPU with real-time task, would be the source of scheduler duration jitter. Thus,
